Survival Analysis

### 2014-05-08 paper.Rnw
Make fixes

Variants of the proportional hazards model can be made by varying the baseline hazard's distribution. For example, if $\lambda_{0}$ follows an exponential distribution, then the hazard function $\lambda$ follows a Weibull distribution. Likewise, if $\lambda_{0}$ is constant, then $\lambda$ follows an exponential distribution.

@@

The range of durations for breastfeeding is from 1 week to 192 weeks. Only 12\% of subjects had breastfeeding durations greater than 36 weeks. If we were to graph $\hat S(t)$, 20\% of the x-axis will contain 88\% of the data, which makes detecting patterns in the data visually very difficult. For this reason, durations greater than 36 weeks will be censored as 36 weeks.

@@

The vertical red dashed line represents the Food and Drug Administration's recommended duration of breastfeeding, 6 months. The steep drop off at 36 weeks is due to the censoring used to make the graphs easier to interpret. The red crosses indicate censored observations and the dashed black line is the 95\% confidence band of the Kaplan-Meier estimator.

@@

We may verify this casual relation by performing a log-rank test assuming $\alpha = 0.05$. The log-rank test compares hazard rates rather than survival rates:

\[ H_0: \Lambda_{ys \leq 12} = \Lambda_{ys > 12} \]
\[ H_a: \Lambda_{ys \leq 12} \neq \Lambda_{ys > 12} \]

>>>>

Variants of the proportional hazards model can be made by varying the distribution of events $f(t)$ or the baseline hazard's distribution $\lambda_0(t)$. For example, if $\lambda_{0}$ follows an exponential distribution, then the hazard function $\lambda$ follows a Weibull distribution. Likewise, if $\lambda_{0}$ is constant, then $\lambda$ follows an exponential distribution. We may define $f(t)$ instead of $\lambda_{0}(t)$ as well because we can derive $\lambda_{0}(t)$ from $f(t)$. Choosing which function to define, the event distribution or baseline hazard rate, is a matter of convenience and preference.

@@

The range of durations for breastfeeding is from 1 week to 192 weeks. Only 12\% of subjects had breastfeeding durations greater than 36 weeks. If we were to graph $\hat S(t)$, 20\% of the x-axis will contain 88\% of the data, which makes detecting patterns in the data visually very difficult. For this reason, durations greater than 36 weeks will be treated as 36 weeks.

@@

The vertical red dashed line represents the Food and Drug Administration's recommended duration of breastfeeding, 6 months. The steep drop off at 36 weeks is due to the truncation used to make the graphs easier to interpret. The red crosses indicate censored observations and the dashed black line is the 95\% confidence band of the Kaplan-Meier estimator.

@@

We may verify this casual relation by performing a log-rank test assuming $\alpha = 0.05$. The hypotheses for this test are:

\[ H_0: \S_{ys \leq 12} = \S_{ys > 12} \]
\[ H_a: \S_{ys \leq 12} \neq \S_{ys > 12} \]
